Fast approximate Bayesian inference of HIV indicators

### 2023-05-19 src/docs_19-05-23-turing/19-05-23-turing.Rmd
Correct LaTeX error #37

```{r, echo=FALSE, fig.cap="Reduced RMSE by 10%, but still a work in progress! Also using Kolmogorov-Smirnov tests, Pareto-smoothed importance sampling, maximum mean discrepancy...", out.width = '80%'}
knitr::include_graphics("depends/second90.pdf")
```

>>>>

```{r, echo=FALSE, fig.cap="Reduced RMSE by 10 percent, but still a work in progress! Also seeing small improvements using Kolmogorov-Smirnov tests, Pareto-smoothed importance sampling, maximum mean discrepancy.", out.width = '80%'}
knitr::include_graphics("depends/second90.pdf")
```
